The Etiology of Cybersecurity

### 2020-08-03 reports/paper_0/main.tex
review abstract

\begin{abstract}
	The objective of this research is lay the foundation for the
	development of a theory that determines (all and only) the possible
	insecure and secure configurations of any abstract system.  Our
	hypothesis is that cybersecurity weaknesses (i.e. errors) are at the
	bottom of the causality chain that leads to cybersecurity attacks.
	Based on this hypothesis, we formulate a scientific (falsifiable by
	experiments) hypothesis that predicts all the weaknesses that lead to
	the presence of cybersecurity weaknesses in the architectural design of
	an abstract system. The mathematical formulation of our hypothesis is
	based on a correlation between the epistemological concepts of
	knowledge, beliefs, and information with the engineering concepts of
	requirements, functional architectures, and channels.  Ultimately, our
	hypothesis allows the definition of the cybersecurity of a system as a
	mathematical formula.  We implemented a prototype cybersecurity risk
	assessment tool that, based on our hypothesis, predicts weaknesses in a UML
	model of a (cyber-physical) system.
\end{abstract}

>>>>

\begin{abstract}
	The objective of this research is to lay the foundations for the
	development of a theory that determines (all and only) the possible
	insecure and secure configurations of any abstract system. We claim
	that cybersecurity weaknesses (i.e. errors) are at the beginning of the
	causality chain that leads to cybersecurity attacks.  We, then,
	formulate a scientific (falsifiable by experiments) hypothesis that we
	use to predict all the weaknesses in the architectural design of an
	abstract system. The mathematical formulation of our hypothesis is
	based on a correlation between the epistemological concepts of
	knowledge, beliefs, and information with the engineering concepts of
	requirements, functional architectures, and channels.  Ultimately, our
	hypothesis allows the definition of the cybersecurity of a system as a
	mathematical formula.  We implemented a prototype cybersecurity risk
	assessment tool that, based on our hypothesis, predicts weaknesses in a
	UML model of a (cyber-physical) system.
\end{abstract}
